Master thesis problem statement: Keyword search over heterogeneous sources

### 2012-12-21 doc/thesis/latex/proposed_solutions.tex
elsevier styles; minor changes

Other way to boost performance is pre-fetching most common queries from time to time (determined manually and/or automatically). Also it's possible have different validity dates for certain fields. if no volatile fields are not explicitly requested, even a very old cache could be used

@@

\subsubsection*{Integrating distributed information efficiently}
Bloom-join (which could be quite transparent and implemented even on DB side (efficient pure SQL is doable for MySQL, and probably for Oracle too) quite almost transparently (a helper function could take the initial query and bloom-filter's bit-vector as parameters).

>>>>

Other way to boost performance is pre-fetching most common queries from time to time (determined manually and/or automatically). Also it's possible have different validity dates for certain fields. If no volatile fields are explicitly requested, even a very old cache could be used.

@@

\subsubsection*{Integrating distributed information efficiently}
Bloom-join (which could be quite transparent and implemented even on DB side (efficient pure SQL is doable for MySQL, and probably for Oracle too) quite transparently (a helper function could take the initial query and bloom-filter's bit-vector as parameters).
